The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: typesetting improvements

Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \begin{tikzcd}
    & & \painting[n+1][\lbrack p,n+1 \rbrack] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][\lbrack 0,p-1 \rbrack]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][\lbrack p,n+1 \rbrack]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] & &
    \painting[n][\lbrack p,n-1 \rbrack] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \udensdash{\restrf[n][\lbrack 0,p-1 \rbrack]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][\lbrack p,n \rbrack] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][\lbrack p,n \rbrack]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

@@

Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$. It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$. Thus, we also include this abbreviation in the definition. Implicitly using in $\cohf[n+1][\lbrack 0,p \rbrack]$ that equalities in a $\Sigma$-type are equivalent to a $\Sigma$-type of the underlying equalities, we altogether have:

@@

    \end{array}                                           \\

@@

@@

  \left(

@@

>>>>

Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $E_n$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \begin{tikzcd}
    & & \painting[n+1][\lbrack p,n+1 \rbrack] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][\lbrack 0,p-1 \rbrack]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][\lbrack p,n+1 \rbrack]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] & &
    \painting[n][\lbrack p,n-1 \rbrack] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \udensdash{\restrf[n][\lbrack 0,p-1 \rbrack]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][\lbrack p,n \rbrack] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][\lbrack p,n \rbrack]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

@@

Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating the dependency as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$. Note however that, due to reasoning with $\U$, we do not need to have $\cohf[n+1][\lbrack 0,p \rbrack]$ depending on a proof of $\cohttype[n][\lbrack 0,p-1 \rbrack]$ as the latter can be proved at once by uniqueness of identity proofs.

It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$. Thus, we also include this abbreviation in the definition. Implicitly using in $\cohf[n+1][\lbrack 0,p \rbrack]$ that equalities in a $\Sigma$-type are equivalent to the $\Sigma$-type of the underlying equalities, we altogether have:

@@

@@

           \end{array}\right.

@@

  \left\{

@@

  \right.
